\subsection{Reliability}
\begin{itemize}
    \item The system should generate accurate results for searches. A message should be displayed if a location cannot be found or the search cannot be performed.
    \item The system should determine user location and display level of accuracy for triangulation.  
    \item The system should generate correct and reasonable routes when provided with two locations.
    \item Users with administration privileges should be able to create, update and remove locations.
    \item Notifications should be sent to all registered users via email or SMS.
\end{itemize}

\subsection{Availability}
\begin{itemize}
    \item The system should always be available.
    \item An Internet connection should be available for the application to communicate with the database.
    \item The application should be connected to the built-in GPS application so that the user's location can be determined.
    \item Users should be notified if the system is not available.
    
\end{itemize}

\subsection{Security}
\begin{itemize}
    \item Communication between the application and the user database should be encrypted.
    \item If a user attempts to log in with invalid credentials, they should not be given access and a failure message should be displayed.
    \item Only users with administration privileges should be able to perform functions that deal with the management of location objects and events.
    
\end{itemize}

\subsection{Maintainability}
\begin{itemize}
    \item The system should be implemented with as little coupling as possible, so that it is easy to add new functions and extend it.
    \item Tests must be built for each module in isolation, in order to determine their functionality. 
\end{itemize}
\subsection{Portability}
    \begin{itemize}
        \item The application should be portable with both Android and iOS platforms.
    \end{itemize}